plyranges: a grammar for transforming genomics data

### 2018-03-26 paper.Rmd
consistency of naming

The _plyranges_ package is available on the Bioconductor project website 
[https://bioconductor.org](https://bioconductor.org) or can be accessed
via Github [https://github.com/sa-lee/plyranges](https://github.com/sa-lee/plyranges).
We aim to continue developing the _plyranges_ package and extend it for use
with more complex data structures  such as the 
_SummarizedExperiment_ class, which can be used for analysing transcriptomic
and variant data. As the _plyranges_ interface encourages tidy data 
practices it integrates well with the principles of the grammar of graphics, 
we aim to use it for the visualisation of multimodal biological datasets.

>>>>

The _plyranges_ package is available on the Bioconductor project website 
[https://bioconductor.org](https://bioconductor.org) or can be accessed
via Github [https://github.com/sa-lee/plyranges](https://github.com/sa-lee/plyranges).
We aim to continue developing the `plyranges` package and extend it for use
with more complex data structures  such as the 
_SummarizedExperiment_ class, which can be used for analysing transcriptomic
and variant data. As the `plyranges` interface encourages tidy data 
practices it integrates well with the principles of the grammar of graphics, 
we aim to use it to prepare data for the visualisation of multimodal biological 
datasets.
